%-----------EXPERIENCE-----------
% \section{EXPERIENCE}
  \customSubHeadingContentStart

    \customSubHeading
    {Associate Manager, Data Analytics \& Engineering}{Mar 2023 – Present}
    \customRoleHeading
    {\href{https://www.bracbank.com/en/}{\textbf{BRAC Bank PLC}}}{ Dhaka, Bangladesh}
    \vspace{-15pt}
      \customItemListStart
        \customItem{\textbf{Designed and launched an in‑house Campaign Management Tool (CMT)} to fully automate customer reward calculation and distribution (cashback, bonus points, digital rewards, annual fee waivers). This is a significant shift from end‑of‑campaign manual processing to instant settlement upon eligible transactions.}
        \customItem{\textbf{Integrated Oracle Data Integrator (ODI)} to replace the legacy system, streamlining multi‑source ingestion and improving data transition speed from source systems to the Data Warehouse by \textbf{at least 30\%.}}
        \customItem{Developed and \textbf{deployed multiple enterprise‑grade Power BI dashboards} with role‑based security and automated refresh schedules, eliminating repetitive manual reporting and saving \textbf{at least 25\% }in team work‑hours.}
      \customItemListEnd

    \customSubHeading
    {Business Intelligence Analyst}{Dec 2022 – Mar 2023}
    \customRoleHeading
    {\href{https://www.foodpanda.com.bd/}{\textbf{Foodpanda Bangladesh}}}{ Dhaka, Bangladesh}
    \vspace{-15pt}
      \customItemListStart
        \customItem{Delivered interactive, drill‑down \textbf{Tableau visualizations} that reduced reporting turnaround from hours to minutes.}
        \customItem{Partnered with cross-functional teams (marketing, ops, finance) to \textbf{define KPIs} and deliver scalable, self-service Tableau dashboards powered by BigQuery, enabling \textbf{real-time performance tracking} and decision-making.}
        \customItem{Conducted deep-dive analysis of high-volume order and campaign data to uncover actionable trends, optimize promotional spend, and improve targeting, resulting in a \textbf{15\% uplift in campaign ROI} across key segments.}
      \customItemListEnd

    \customSubHeading
    {Senior Software Engineer}{Oct 2022 – Dec 2022}
    \customRoleHeading
    {\href{https://kovair.com/}{\textbf{Kovair Software}}}{ Dhaka, Bangladesh}
    \vspace{-15pt}
    \customItemListStart
  
        \customItem{\textbf{Led end-to-end development} of \textit{\href{http://www.raspberryerp.com}{\textbf{Raspberry ERP}}} for large-scale warehouse, inventory, audit, and supply-chain operations across Indian fertilizer firms, managing cross-functional teams and aligning with client workflows.}
        
        \customItem{Designed \textbf{backend data workflows} and RESTful APIs to enable real-time inventory tracking, audit trail generation, and seamless integration with ERP modules, enhancing operational accuracy and system reliability.}
        
    \customItemListEnd

    \customSubHeading
    {Software Engineer}{May 2021 – Sep 2022}
    \customRoleHeading
    {\href{https://kovair.com/}{\textbf{Kovair Software}}}{ Dhaka, Bangladesh}
    \vspace{-15pt}
      \customItemListStart
      
        \customItem{\textbf{Optimized ETL workflows} using MS SQL Server and SSIS, \textbf{reducing batch run time by 30\%} and enhancing reliability of reconciliation and compliance reporting through robust data validation and error handling.}
        
        \customItem{\textbf{Built custom T‑SQL stored procedures and tuned queries for faster access} to inventory, audit, and forecasting datasets; developed role-specific dashboards for reconciliation, compliance, and dispatch planning.}
    
      \customItemListEnd
    
  \customSubHeadingContentEnd
\vspace{-10pt}